Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/results.tex
add to repro sub-section (c)  in results

 Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
 A key element is professional software management and engineering, and the central technology solution is version control. 
 Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
 Another key element of transparent and reproducible computational modeling is \emph{automation}.
Automating every step means \emph{turning protocols into code.}
For example, simulations are launched with parameters fed from a configuration file rather than an interactive prompt, and all figures and plots are produced by writing scripts, rather than pointing-and-clicking on a graphical interface. 
The goal is to create complete ``recipes'' in code, which can be run, versioned, and shared.

Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.
As in our previous papers, it is possible to reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo.
[LIST, EXPLAIN, CITE ARCHIVES] 
\pygbe is openly developed and shared under the BSD3-clause license via its repository at \url{https://github.com/barbagroup/pygbe}.

>>>>

 Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
 A key element is professional software management and engineering, and the central technology solution is version control. 
 Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility. 
 Moreover, all our research software is developed in the open, and shared under permissive public licenses, such as BSD-3 or MIT License. 
 These open licenses permit all uses, as well as derivative works, only subject to attribution.
 Another key element of transparent and reproducible computational modeling is \emph{automation}.
Automating every step means \emph{turning protocols into code.}
For example, simulations are launched with parameters fed from a configuration file rather than an interactive prompt, and all figures and plots are produced by writing scripts, rather than pointing-and-clicking on a graphical interface. 
The goal is to create complete ``recipes'' in code, which can be run, versioned, and shared.

Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short, and we have been doing this for many years and improving the process iteratively. 
The basic steps were already contained in the ``Reproducibility PI Manifesto'' of 2012 \cite{barba2012manifesto}, where Barba pledged to always share a manuscript's data, plotting scripts and figures under CC-BY (Creative Commons Attribution license).
Notably, this makes the figures re-usable by readers, without requiring them to ask permissions from the publisher, even if there was a transfer of copyright of the paper (the figures are included in the paper under the conditions of the public license). 
We later extended the practice to include all other digital artifacts associated with the results, beyond secondary data and figures. 
As in our previous papers, readers can reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo. 
They include Jupyter notebooks with all the plotting code, and also the manually digitized data from the figures in the source articles for our replication cases.
Barba and Thiruvathukal, 2017 \cite{BarbaThiruvathukal2017}, explain that it is \emph{not enough} to provide these materials in a GitHub repository (the owner of a repository is always able to delete it), and one should deposit the reproducibility packages in an archival service providing a global identifier and permanent link (like a digital object identifier, DOI).
%[LIST, EXPLAIN, CITE ARCHIVES] 
The repository for this paper is at \url{https://github.com/barbagroup/pygbe_validation_paper}, which also includes the manuscript source files in LaTeX.
The software repository for \pygbe is at \url{https://github.com/barbagroup/pygbe}.
